Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-06 paper/manuscript/appendix.Rmd
tweaks to appendix formatting

---
title: Appendix to 'Detecting social information in a dense database of infants’ natural
  visual experience'
date: "`r Sys.Date()`"
output:
  pdf_document: default
---

@@

# Distribution of faces and hands in the visual field
We explored where in the visual field children tended to see faces and hands, suspecting that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank (2012). 
As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located (see Figure C1). 
However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ visual environment from 6 months of age.

@@

p1 <- ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Face detections") + 
  theme(legend.position= 'none')

p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Hand detections") + 
  theme(legend.position= 'none')
```

@@

```{r det_perf_by_locations, fig.width=6.5, fig.height=3.0, fig.cap="F-score of OpenPose hand and face detections in the gold sample by location. Size indicates number of detections per location: minimum = 55 (car); maximum = 1753 (living room)."}
p1 <- ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  ylab('F-score') + ggtitle("Face detections") +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(0,1)

p2 <- ggplot(prf_by_location_hands, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  ylab('F-score') + ggtitle("Hand detections") +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(0,1)

@@

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse()

>>>>

---
title: Appendix to 'Detecting social information in a dense database of infants’ natural
  visual experience'
date: "`r Sys.Date()`"
output:
  papaja::apa6_pdf: default
---

@@

# Distribution of faces and hands in the visual field
We explored where in the visual field children tended to see faces and hands, suspecting that these distributions might become wider as children grow older and learn to locomote on their own, following preliminary analyses from Frank (2012). 
As expected, faces tended to appear in the upper visual field in contrast to hands, which tended to be more centrally located (see Figure).
However, we found little evidence for any changes in the positions of faces and hands across age, suggesting that this is a relatively stable property of infants’ visual environment from 6 months of age.

@@

p1 <- ggplot(prf_by_age_faces, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  theme_few(base_size=12) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Face detections") + 
  theme(legend.position= 'none')

p2 <- ggplot(prf_by_age_hands, aes(x=age_day_bin, y=f, col=child_id, size=num_detect)) +
  geom_point(alpha=.5) +
  geom_smooth(span=20, alpha=.1)  +
  ylim(0,1) +
  theme_few(base_size=12) +
  ylab('F-score') + xlab('Age (months)') +
  ggtitle("Hand detections") + 
  theme(legend.position= 'none')
```

@@

```{r det_perf_by_locations, fig.width=6.5, fig.height=3.0, fig.cap="F-score of OpenPose hand and face detections in the gold sample by location. Size indicates number of detections per location: minimum = 55 (car); maximum = 1753 (living room)."}
p1 <- ggplot(prf_by_location_faces, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  theme_few(base_size=12) +
  ylab('F-score') + ggtitle("Face detections") +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(0,1)

p2 <- ggplot(prf_by_location_hands, aes(x=Location, y=f, col=Location, size=num_detect)) +
  geom_point(alpha=.5) +
  theme_few(base_size=12) +
  ylab('F-score') + ggtitle("Hand detections") +
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  ylim(0,1)

@@

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  scale_y_reverse() +
  theme_few(base_size=12)

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  scale_y_reverse() +
  theme_few(base_size=12)

### 2022-01-06 paper/manuscript/manuscript_dec2021_apa_blinded.Rmd
tweaks to appendix formatting

keywords          : "social cognition; face perception; infancy; head cameras; deep learning"
wordcount         : "4681"

@@

## Variability with motor development milestones
How does the social information in view change as a function of motor development? One idea is that children’s ability to stand and move on their own may fundamentally change the visual social information that they see (e.g., facial expressions, gaze cues, pointing)  [@walle2014infant; @walle2016] relative to infants who are still sitting and crawling.  Indeed, in in-lab studies, children's in-the-moment posture -- and that of their caregiver -- is a strong predictor of the visual social information that children see [@franchak2017see; @long2021automated].

@@

ggplot(avg_area_by_age, aes(x=age_day_bin, y=log(avg_area), col=child_id, size=num_detect)) +
  geom_point(alpha=.1) +
  facet_grid(~label) +
  geom_smooth(method='lm') + 
  ylab('Log area (average proportion of frame)') +
  xlab('Age (in months)') +
  scale_color_brewer(palette="Dark2", name = "Child") +
  guides(size = FALSE)
```

@@

```{r}
CV_faces_plot <- ggplot(CV_faces, aes(x=age_day_bin, y = CV, size=num_detect, color=child_id)) +
  geom_point(alpha=.15) + 
  facet_wrap(~position)  +
  geom_smooth(method='lm') +
  ggtitle('B.') +
  scale_color_brewer(palette='Dark2', name='Child') + 
  ylab('Coefficient of variation') +
  xlab('Age (in months)') +
  guides(size = FALSE) 
```

>>>>

keywords          : "social cognition; face perception; infancy; head cameras; deep learning"
wordcount         : "X"

@@

## Variability with motor development milestones
How does the social information in view change as a function of motor development? One idea is that children’s ability to stand and move on their own may fundamentally change the visual social information that they see (e.g., facial expressions, gaze cues, pointing)  [@walle2014infant; @walle2016infant] relative to infants who are still sitting and crawling.  Indeed, in in-lab studies, children's in-the-moment posture -- and that of their caregiver -- is a strong predictor of the visual social information that children see [@franchak2017see; @long2021automated].

@@

ggplot(avg_area_by_age, aes(x=age_day_bin, y=log(avg_area), col=child_id, size=num_detect)) +
  theme_few(base_size=12) +
  geom_point(alpha=.1) +
  facet_grid(~label) +
  geom_smooth(method='lm') + 
  ylab('Log area (average proportion of frame)') +
  xlab('Age (in months)') +
  scale_color_brewer(palette="Dark2", name = "Child") +
  guides(size = FALSE)
```

@@

```{r}
CV_faces_plot <- ggplot(CV_faces, aes(x=age_day_bin, y = CV, size=num_detect, color=child_id)) +
  theme_few(base_size=12) +
  geom_point(alpha=.15) + 
  facet_wrap(~position)  +
  geom_smooth(method='lm') +
  ggtitle('B.') +
  scale_color_brewer(palette='Dark2', name='Child') + 
  ylab('Coefficient of variation') +
  xlab('Age (in months)') +
  guides(size = FALSE) 
```
